---
title: "BIO247 Exam 1"
author: "Jonathan Grabowski"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Part 1 - Written

## Problem 1

There is a difference between being reproducible and being robust. If a study is reproducible, a person or group of people should be able to follow the exact same steps used in the study and do the exact same calculations to get a similar result. If a study is robust, a person or group of people follow the same steps used in the study, but they change something in the study like a protein being studied, use the same calculations as the study, and get the same results.  

## Problem 2

On last page of physical copy of exam.

## Problem 3

I believe that this study is reproducible, but I do not think it is robust. I think this study is reproducible because the authors tell you that they are studying public attitudes towards snakes and how they measured certain characteristics of there study like behavioral intent. They also mention that this study was done on a campus in the southeastern United States. Using this information, others could reproduce this study in the exact same location using the exact same methods and get the same result, which would make this study reproducible. However, if this study was done on a different college campus but used the same methods to examine the public attitudes towards snakes, the results could possibly be different due to the fact that people will have different opinions on snakes, which would make the study non-robust. 

## Problem 4

I believe that this study is not reproducible or robust. I think this study is not reproducible because the authors tell you that they used datasets from the RTCGA library, however, they do not tell you which datasets they used in their study. They tell you which type of datasets they used (methylation data, histone modification data, etc.), but they don't specifically tell you which dataset they used. I think this study is not robust because if different data were used to make a model like the authors did, I do not think that they would get the same result. I would have to see another study use the same methods as this study, but use different data and get a similar result to conclude if this study was really robust.  

# Part 2 - Practical

I am going to make a vector called interact in which the word interactions is repeated 25 times using rep(). Then, I will make a vector called Suffixes that contains suffix_1 and suffix_0. Then I will make a for loop to apply one of the suffixes to the word interaction. The first suffix will be applied to the first element in the interact vector. The second suffix will be applied to the second element in the interact vector. This will happen until the each element in the interact vector has a suffix. 

## Problem 5
```{r cars}
interact <- rep("interactions",25)

Suffixes <- c("suffix_1", "suffix_0")

for (each in interact) {
  interactions <- paste(interact, Suffixes, sep=" ")
}

# Part of this solution was sourced from the rmd file created for BIO-247/Lecture/R part 4
```

## Problem 6

I am going to upload the data called GMB_data by using the function csv(). Next I will pull the ggplot2 package from my library. Next I use the ggplot function, with Total.Score being x in the aes argument then add on geom_density to create a 
density plot of the Total.Score column. 

```{r}
GBM_data <- read.csv("GBM_data.csv")

library(ggplot2)

ggplot(GBM_data, aes(x=Total.Score)) + geom_density()
```

## Problem 7

I am going to use the cut function to make a threshold in the dataset.

I was unable to use the cut function to make a threshold in the dataset. Looking at the density plot from Problem 6, I would make a cutoff after the first jump in density because it is large. I would do this because the Total.Scores.

The code below is the code that I tried using to make a threshold.

```{r}
#GBM_data$Total.Score <- cut(GBM_data$Total.Score, breaks = 0:145)
```

## Problem 8

I am going to use the function gsub() to get rid of junk characters from the Paper.ID column in the dataset GBM_data. Then I will use the strsplit function to break the column into a vector of lists, the unlist function to make the vector not a vector of lists, the unique function to get all of unique papers in the dataset, the length function to find the exact number of unique papers in the dataset, and print to print the exact number of unique papers.

Since I was unable to make a threshold in the last problem, the code below gives the unique papers for the entire dataset.

```{r}
GBM_data$Paper.ID <- gsub("\\[", "", GBM_data$Paper.ID)
GBM_data$Paper.ID <- gsub("\\]", "", GBM_data$Paper.ID)
GBM_data$Paper.ID <- gsub("\\'", "", GBM_data$Paper.ID)
GBM_data$Paper.ID <- gsub(" ", "", GBM_data$Paper.ID)

print(length(unique(unlist(strsplit(GBM_data$Paper.ID, ",")))))

# Part of this solution was sourced from the rmd file created for BIO-247/Lecture/R part 4
```
