---
title: "R part 4"
author: "Jonathan Grabowski"
date: '2022-09-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A # symbol in the box where code goes in an Rmarkdown can be used to make R read the line of code as a comment. 

```{r}
#shirt <- "red"
shirt <- "yellow"
#shirt <- "green"
#shirt <- "blue"
#shirt <- "white"
```

The loop below is made to tell a person to eat a specific food if their shirt is a certain color.

```{r}
if (shirt =="red") {
  print("apple")
} else if (shirt == "yellow") {
  print("banana") 
} else if (shirt == "green") {
  print("watermelon")
} else if (shirt == "blue") {
  print("blueberries")
} else  {
  print("egg whites")
} 
```

I generated a random number from 1 to 1000 and named it stop. Then, I made a while loop that will print "pop goes the weasel" when the number is reached.

```{r}
stop <- sample(1:1000, 1)

num = 0
while (num > stop){
  num <- num + 1
}
print ("pop goes the weasel")
```

I created a vector with the words "Pop", "goes", "the", "weasel" and named the vector vect1. Then, I created a loop that prints each word in the vector at the same time.

```{r}
vect1 <- c("Pop","goes","the","weasel")
for (each in vect1){
print(each)
}
```

The gsub function will remove junk characters. I removed blank spaces, left brackets, right brackets, and quotation marks from the Paper ID column in the dataset Test_V_output.

```{r}
Test_V_output$`Paper ID`<- gsub("\\[", "", Test_V_output$`Paper ID`)
Test_V_output$`Paper ID`<- gsub("\\]", "", Test_V_output$`Paper ID`)
Test_V_output$`Paper ID`<- gsub("\\'", "", Test_V_output$`Paper ID`)
Test_V_output$`Paper ID`<- gsub(" ", "", Test_V_output$`Paper ID`)
```

This code will print the number of unique papers in the Paper ID column in the dataset Test_V_output.
```{r}
print(length(unique(unlist(strsplit(Test_V_output$`Paper ID`, ",")))))
```





